Search-based Synthesis of Network Intrusion Detection Rules

### 2019-10-03 paper/paper.tex
minor comments

\tname{} uses a modified version of Suricata to measure distance. It
updates the rule set that the modified version of Suricata analyses,
injects the traffic on the network, and monitors the execution. Each
rule option has an associated \CodeIn{eval} function in code. \tname{}
monitors the execution of these functions to identify how far it is
from returning true, which indicates it is closer to trigger the
action associated with the rule. For the example above,
\Fix{Lucas/Guilherme, it would be good to show how this looks like in
  code}

>>>>

\tname{} uses a modified version of Suricata to measure distance. It
updates the rule set that the modified version of Suricata analyses,
injects the traffic on the network, and monitors the execution. Each
rule option has an associated \CodeIn{eval} function in code. \tname{}
monitors the execution of these functions to identify how far it is
from returning true, which indicates it is closer to trigger the
action associated with the rule. 
\Luc{Originalmente, o suricata interrompe a checagem de uma regra quando alguma das opções não dá match com o pacote analisado. O código fonte foi alterado para que as regras sempre tenham todas as suas opções verificadas. A função de verificação de uma opção retorna um booleano indicando se o valor da opção na regra corresponde ou não ao valor da opção no pacote. Para opções cujos valores são numéricos, alteramos o código fonte para obter a diferença entre os valores da opção na regra e no pacote.}
\Fix{Lucas/Guilherme, it would be good to show how this looks like in
  code}
